---
title: "LP Brewery"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Probelm Statement

#### Build a report for LP Brewery telling them all the information from their new problem with Dantzig and their previous problem before Dantzig <http://learn.codingdojo.com/m/147/6683/49453>.

##### Recipes for Hopatronics IPA, American Kolsch, and Barrel-Aged Dantzig

  Beverage     | Corn (pounds)  |  Hops (ounces) |  Malt (pounds) |  
-------------- | -------------  | -------------- | -------------- | 
Hopatronics IPA|       5        |       4        |        35      |     
American Kolsch|       15       |       4        |        20      |    
Dantzig        |       10       |       4        |        15      |     
   Quantity    |      480       |      160       |       1190

##### Profit bar chart
```{r beverage, echo=FALSE}
library("lpSolve")
f.obj <- c(13, 23, 30)
barplot(f.obj, main="Profits $", names.arg=c("Hopatronics IPA","American Kolsch", "Dantzig"))
```

##### Each of the kegs takes the following hours of labor, we have 5 employees full-time

 Beverage      |    Hours  
-------------- | -------------
Hopatronics IPA|       5       
American Kolsch|       10       
Dantzig        |       20       
Total hours of labor     | 1200

##### Total hours of labor is 1200, which means each employee has to work 8 hour per day for a month
#### How can brewer maximize profits? 
##### 1. Before Dantizig
```{r lp, echo=FALSE}
f.obj <- c(13,23)
# Each row represent Corns, Hops, Malt, Hours.
f.con <- matrix(c(5,15,
                  4,4,
                  35,20,
                  5, 10), nrow = 4, byrow = TRUE)

# Create a list of directions
f.dir <- c("<=","<=","<=", "<=")

# Create a list of right hand side for the constraints
f.rhs <- c(480,160,1190, 1200)

sol <- lp("max", f.obj, f.con, f.dir, f.rhs,compute.sens = TRUE)

```
 * Plotting the constraints
```{r}
library(ggplot2)
ggplot(data.frame(x = c(0, 100)), aes(x = x)) + 
  stat_function(fun = function(x) {(480 - 5*x)/15}, aes(color = "Corns")) + 
  stat_function(fun = function(x) {(160 - 4*x)/4 }, aes(color = "Hops")) + 
  stat_function(fun = function(x) {(1190 - 35*x)/20 }, aes(color = "Malts")) + 
  stat_function(fun = function(x) {(1200 - 5*x)/10 }, aes(color = "Hours")) + 
  theme_bw() + 
  scale_color_discrete(name = "Constraints")
```
 

 * The optimum value of Hopatronics IPA and American Kolsch to maximize profit
```{r sol, echo=FALSE}
# Compute optimum value for each beer
Best_sol <- sol$solution
names(Best_sol) <- c("Hopatronics IPA", "American Kolsch") 
print(Best_sol)
```
 * The maximum profit at optimal point 
```{r obj, echo=FALSE}
cat("Total profit: ", sol$objval, sep="")
```
 * The duals of constraints and reduced costs of variables
```{r duals, echo=FALSE}
sol$duals
```
 * The sensitivity analysis of LP 
```{r sa, echo=FALSE}
sol$duals.from
sol$duals.to
sol$sens.coef.from
sol$sens.coef.to
```

 
##### 2. After Dantizig
##### After LP Brewery coming up with a hot new brew called The Barrel-Aged Dantzig. They had to think about allocating its personnel to the different manufacturing processes, and the following is an analysis report after adding the new brew. 
 
```{r lp1, echo=FALSE}
f1.obj <- c(13, 23, 30)


# Each row represent Corns, Hops, Malt, Hours.
f1.con <- matrix(c(5,15,10,
                  4,4,4,
                  35,20,15,
                  5, 10, 20), nrow = 4, byrow = TRUE)

# Create a list of directions
f1.dir <- c("<=","<=","<=", "<=")

# Create a list of right hand side for the constraints
f1.rhs <- c(480,160,1190, 1200)

sol1 <- lp("max", f1.obj, f1.con, f1.dir, f1.rhs,compute.sens = TRUE)


```

 * The optimum value of Hopatronics IPA and American Kolsch to maximize profit
```{r sol1, echo=FALSE}
# Compute optimum value for each beer
Best_sol1 <- sol1$solution
names(Best_sol1) <- c("Hopatronics IPA", "American Kolsch", "Dantzig") 
print(Best_sol1)
```
 * The maximum profit at optimal point 
```{r obj1, echo=FALSE}
cat("Total profit: ", sol1$objval, sep="")
```
 * The duals of constraints and reduced costs of variables
```{r duals1,echo=FALSE}
sol1$duals
```
 * The sensitivity analysis of LP 
```{r sa1, echo=FALSE}
sol1$duals.from
sol1$duals.to
sol1$sens.coef.from
sol1$sens.coef.to
```


